Figure 1.Luminal Study Groups

### 2023-03-08 reports/manuscript/Figure1.Rmd
Add filtering
Add figure legend

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
#.libPaths("/Users/vilkal/Applications/miniconda3/envs/Paulos_repo/lib/R/library")

@@

```{r Load data}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(magick)
  library(uwot)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

pal <- c( "#0072B2", "#009E73","#D55E00", "#CC79A7", "#E69F00", "#999999")
taxa_pal <- c(RColorBrewer::brewer.pal(8,"Pastel2"),RColorBrewer::brewer.pal(8,"Pastel1"),"grey90")
# show_col(pal)
```

@@

  temp <- t(t(2^x-1)/colSums(2^x-1))

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results    = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width  = 6.6929133858,
  fig.align  = "center",
  fig.path   = "./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
#.libPaths("/Users/vilkal/Applications/miniconda3/envs/Paulos_repo/lib/R/library")

@@

```{r Load-data}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(magick)
  library(uwot)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

pal <- c( "#0072B2", "#009E73","#D55E00", "#CC79A7", "#E69F00", "#999999")
taxa_pal <- c(RColorBrewer::brewer.pal(8,"Pastel2"),RColorBrewer::brewer.pal(8,"Pastel1"),"grey90")
# scales::show_col(taxa_pal)
```

@@

  dim(x)
  x <- x[ rowSums(x>0) >= 3 ,  ]
  #x_ <- x[ rowSums(x>0) ,  ]
  dim(x)
  temp <- t(t(2^x-1)/colSums(2^x-1))

@@

**Figure 1. Characterization of a highly diversemicrobiome in cervicovaginal (luminal) samples from Kenyan sex workers.** Cervicovaginal lavage (luminal) and ectocervical tissue study samples were assessed by 16S rRNA sequencing, gene expression, and protein profiling. **a** Schematic drawing depicting the sampling scheme and the resulting omics datasets. **b** Bar plots of alpha diversity indices and taxonomy profiles for each individual luminal sample. Color-coded squares above the stacked bar plots indicate bacterial vaginosis (BV, binned Nugent’s scores): Gray: negative, orange: intermediate, red: positive; and HIV diagnosis: Gray: HIV seronegative, red: HIV seropositive. Two12-SNN graphs were constructed using:
**c** Louvain community detection algorithm, and d Uniform Manifold Approximation (UMAP). The two graphs were overlayed in color with the predefined luminal study groups. The undirected edges are included in gray connecting the nodes
